Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-19 WRITEUP/ms.tex
done dyn modelling

\section{HST astrometry} %DONE
We obtain HST images from the Hubble Legacy Archive with
a goal to understand the origins of the emission detected
in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
resolution as the reference coordinate frame to align the optical (V$-$band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$-$2") of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. Such astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

@@

\begin{figure}[tbph]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$=0.6537, which is approximately the line center
considering the asymmetry is as a result of differential lensing.
A more detailed discussion of differential lensing effect is presented in
\Sec{differential} and the magnification factors for various kinematic
components are listed in \Tab{mag}.
 \label{fig:CO21spec}}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
% [height=1in,width=5in]
\includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 0, clip, width=0.22\textwidth]{../Figures/F555W_REDBLUE.eps}
\caption{
An overlay of the velocity-integrated \bco emission on the HST V$-$band (F555W)
image. The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295. Right: contours
are color-coded to represent the red and blue wings of the emission.
\label{fig:CO21mom}}
\end{figure}

@@

\subsection{Photometry} \label{sec:photometry} %DONE
We compile \mir to \fir broadband photometry from various
catalogs available on the NASA/IPAC Infrared Science
Archive (IRSA) in \Tab{photometry}. These data were obtained from
the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
Wide-field Infrared Survey Explorer (WISE; \citealt{Wright10a}),
{\it Infrared Astronomical Satellite} (IRAS; \citealt{Neugebauer84a}), and
the Multiband Imaging Photometer (MIPS; \citealt{Rieke04a}) and
Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
\spitzer. We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
Spitzer Heritage Archive. We perform aperture photometry on
the channel 1 image to extract flux density at 3.6\,$\mu$m
since it is not available from the IRSA archive.

The emission in the IRAC images is slightly extended. We thus use the
HST image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy. We use the average
FWHM found by fitting a Gaussian profile to several field stars
using \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the IRAC imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
The details of the SED modeling is presented in \Sec{SED}.

Extraction of the {\it Herschel}/SPIRE photometry was
carried out using SUSSEXTractor within Herschel Interactive
Processing Environment (HIPE; \citealt{Ott10a})
over the Level 2 maps obtained from the Herschel Science Archive.
These maps were processed by the SPIRE pipeline
version 13.0 within HIPE. The SUSSEXtractor task estimates
the flux density from an image convolved with a kernel
derived from the SPIRE beam. The flux density
measured by SUSSEXtractor is additionally confirmed
using the Timeline Fitter. This task performs photometry
by fitting a 2D elliptical Gaussian to the Level 1 data at the
source position given by the output of SUSSEXtractor.

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{sec:lensmodel} %DONE
At the angular resolution of the \bco data, the images are resolved
but not within the multiply lensed emission (i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Model of each slice in \Fig{model} thus provides
properties on the intrinsic kinematics. The slices
are obtained by binning the data (over the full linewidth
$\sim$700\kms; see \Sec{CO21}) by five channels (i.e., into seven slices)
 to increase the SNR.

The lens mass distribution is modeled using a singular isothermal
ellipsoid (SIE) profile, which is described by five free parameters: the
positional offset in R.A. and Dec. relative to an arbitrary chosen
fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
position angle. We use the VLA radio continuum emission toward
the foreground galaxy to initialize the positional offset. We impose a
uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec., which is
motivated by the astrometry uncertainties in the VLA image as well as
the uncertainties provided by previous SIE lens model (C06).
We initialize the Einstein Radius based on the model parameters reported by C06
and impose a uniform prior using $\pm$3$\sigma$ from their uncertainties.
The sources are modeled using elliptical Gaussian profiles, which are
parameterized by six free parameters: the positional offset in R.A.
and Dec. relative to the lens, the intrinsic flux density, the effective
radius, the axial ratio, and the position angle. The position of each source
is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
and the effective radius is allowed to vary from 0\farcs01$-$2".

% Check with Shane
Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF). In each model, we employ
$\sim$50,000 samples as the initial ``burn-in'' stage to stabilize the Markov
chains (which we then discard). We use the final $\sim$5,000
samplings to determine the posterior probability distributions. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

We first obtain a preliminary lens model for each channel slice independently,
where their lens parameters are allowed to vary and are initialized according
to the aforementioned way. We obtain the final model
by repeating the modeling over each slice but fixing their lens parameters
according to the overall median in the preliminary models, as listed in \Tab{lens}.
This ensures that all models share the same lens profile.
The magnification factor is determined by taking the ratio
between the image plane flux of the model and the source plane flux.
The best-fit magnification factors are listed in \Tab{model}.

@@

\subsubsection{Interpretation and Caveats} \label{sec:caveat} %DONE
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient in the source plane, which is
indicative of a disk geometry. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

@@

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
\input{table_magFactor}
Previous lens models of RXJ1131 find conspicuous
differential lensing effect across H-Band, V-band, and I-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission, arising from \SF.
The highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO, where the red wing
of \bco is apparently much brighter than that in the blue wing, consistent 
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).

\subsection{\bco Dynamical modeling} \label{sec:dynamics}
Based on the the source plane position of each kinematic components from the
lens model, a clear symmetric velocity gradient is seen, which is suggestive
of a rotating disk.
Assuming the observed velocities of the respective channels
correspond to solely the tangential components (i.e. $\theta$ = 0), we extract
the major axis along the best-fit slice across these source plane positions,
which is along PA of 121\degr.
We attempt to characterize the molecular gas kinematics using an empirically motivated disk model (e.g. Courteau97, Peuch+08, Miller+11):
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{\rm a} \arctan(\frac{R}{R_{\rm t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center, $V_{\rm a}$ is the asymptotic velocity, and $R_{\rm t}$ is the ``turnover'' radius at which the rotation curve
becomes flat. We perform non-linear least square fitting using an orthogonal distance regression to find the best-fit $V_a$, $r_t$, $V_0$, taking into account
errors in both velocity and distance offset (see \Fig{PV}). We also place an upper limit on $r_t$ $<$ 15 kpc (Miller+11, Genzel+??, Puech+08?) to keep this
parameter physical. We then estimate the uncertainties associated with best-fit parameters using a Monte Carlo simulation of 500 iterations, perturbing
the velocity and physical separation according to a random Gaussian distribution of width/sigma based on the input uncertainties on
the data. Using this model, we find $V_a$ = 975$\pm$387, $r_t$ = 10.6$\pm$5.7,
and $V_0$ = 28$\pm$40. We note, however, that since emission is not detected beyond the flat regime of the rotation curve (Figure \ref{fig: PV}), the asymptotic velocity is
poorly constrained. In particular, $V_a$ and $r_t$ are highly correlated with a Pearson coefficient $r$ = 0.998 between the two, and 0.027 between $V_a$ and $V_0$.

While a symmetric velocity field in the source plane is consistent with a rotating disc, such is insufficient to conclude a rotating disk morphology. Additional characteristics such
as peak velocity dispersion at the center of a galaxy and a ``spider'' diagram are needed. Based on the reconstructed source plane in the optical/NIR emission, C06 find that a
n=1 Sersic profile is best fit their model or is it the reconstructed emission (TBD).

The frequently used V$_{\rm max}$ (maximum measured velocity) is not equivalent to the
asymptotic value, Va, a mathematical extrapolation and typically not reached in
the observed rotation curve. Estimates of Va can depend critically on how well
the central region and turn over of the rotation curve are constrained. For the
remaining analysis, we adopt the asymptotic limit as a proxy to the rotation
curve. We also note that typical studies of the Tully-Fisher relation uses V$_2.2$ (at 2.2 $\times$ disc scalelength $\sim$ 1.375 half-light radius $\sim$ 0.7R$_opt$) as the rotation
velocity since this would be the radius at which the velocity of a pure
exponential disc peaks at. However, our source appears to be a disturbed
rotator, albeit coarse resolution. Hence, rather than adopting V$_2.2$, we use the
asymptotic value from the best-fit arctangent model. The half light radius in the
optical is ~xx kpc (from C06; converted in to our cosmology, but BJB 8 kpc
across?).

If we adopt the best-fit parameters, we find a dynamical mass of $M_{\rm dyn}$($<$blah kpc) sin$^2 i$ = BLAH \Msun. Consider the line widths using the separation between
the red- and blue- shifted emission of the \bco line profile of $\Delta v_{\rm sep}/2 \sim$ blah \kms and a source size of blah kpc, we find a dynamical mass of $M_{\rm dyn}$
sin$^2 i$ = BLAH \Msun. If we adopt the inclination angle using the morphological axis ratio from the
reconstructed optical image reported by C06, where the minor axis is 1\farcs8 and the major axis is 3\farcs3.25, then we find an inclination angle of 56.4
\degr. Then $M_{\rm dyn}$\,=\,BLAH. The inclination angle is consistent with the observed unobscured AGN and an observable double peak line profile.

We note, however, that large differences (up to $\gtrsim$10 deg) can be found between such kinematically-derived inclinations and the ones inferred from the morphological
axis ratio (e.g., Chemin et al. 2006). We caution that this analysis is based on limited spatial resolution data and will been verified by future higher-resolution observations.

\subsection{SED modeling} \label{sec:SED}
We extrapolated a power-law to 24 \micron to decompose the flux
at 24 \micron in MIPS.

We fit modified blackbody functions to
to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt κν = 2.64 m2 kg−1 at 125 μm (rest frame; Dunne et al. 2003).)
We added blah\% calibration uncertainties on the PdBI data.

We check convergence of our chains by requiring that the autocorrelation length for each model parameter is several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
Compared with the version of this code used by Riechers et al. (2013), several improvements have been made. First, we have added the ability to impose upper and lower limits as well as Gaussian priors on the model parameters. These additions are useful for analyzing poorly constrained data, such as when we consider fits to only the SPIRE photometry in Section 3. Second, instead of treating the instrument response as a delta function in wavelength, we now fully model the wavelength response of each instrument. We have applied this improved code to FLS 3, and find that the resulting changes in the model parameters are well within the quoted uncertainties.

% upper limit using decomposed 24 um
% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
% parameter estimation problem
For these parameter estimation problems using MCMC to sample,
the full answer is the full joint posterior PDF.
We here report the summary statistics (global mode (where min. chi),
marginal mode (in log file),
posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.

\subsection{ISM properties}
We correct for lensing magnification using the median among our models ($\mu_{\rm L}$=BLAH).
Assuming a Salpeter initial mass function, we find the SFR of blah using the \fir luminosity after corrected for lensing .
\subsection{Gas Mass}
\subsection{Source Extent}
Compared to HST:

@@

>>>>

\section{HST astrometry} %DONE
We obtain {\it HST} images from the Hubble Legacy Archive with
a goal to understand the origins of the emission detected
in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
resolution as the reference coordinate frame to align the optical (V$-$band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. Such astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

@@

\begin{figure}[tbph]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$=0.6537, which is approximately the line center
considering the asymmetry is as a result of differential lensing.
A more detailed discussion of differential lensing effect is presented in
\Sec{differential} and the magnification factors for various kinematic
components are listed in \Tab{model}.
 \label{fig:CO21spec}}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
% [height=1in,width=5in]
\includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 0, clip, width=0.22\textwidth]{../Figures/F555W_REDBLUE.eps}
\caption{
An overlay of the velocity-integrated \bco emission on the {\it HST} V$-$band (F555W)
image. The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295. Right: contours
are color-coded to represent the red and blue wings of the emission.
\label{fig:CO21mom}}
\end{figure}

@@

\subsection{Photometry} \label{sec:photometry} %DONE
We compile \mir to \fir broadband photometry from various
catalogs available on the NASA/IPAC Infrared Science
Archive (IRSA) in \Tab{photometry} with aperture corrections
when warranted. These data were obtained from
the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
Wide-field Infrared Survey Explorer (WISE; \citealt{Wright10a}),
{\it Infrared Astronomical Satellite} (IRAS; \citealt{Neugebauer84a}), and
the Multiband Imaging Photometer (MIPS; \citealt{Rieke04a}) and
Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
\spitzer.
We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
Spitzer Heritage Archive and perform aperture photometry on
the channel 1 image to extract flux density at 3.6\,$\mu$m
since it is not available from the IRSA archive.

The emission in the IRAC images is slightly extended. We thus use the
HST image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the IRAC imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

Extraction of the {\it Herschel}/SPIRE photometry was
carried out using SUSSEXTractor within Herschel Interactive
Processing Environment (HIPE; \citealt{Ott10a})
over the Level 2 maps obtained from the Herschel Science Archive.
These maps were processed by the SPIRE pipeline
version 13.0 within HIPE. The SUSSEXtractor task estimates
the flux density from an image convolved with a kernel
derived from the SPIRE beam. The flux density
measured by SUSSEXtractor is additionally confirmed
using the Timeline Fitter, which performs photometry
by fitting a 2D elliptical Gaussian to the Level 1 data at the
source position given by the output of SUSSEXtractor.

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{sec:lensmodel} %DONE
At the angular resolution of the \bco data, the images are resolved
but not within the multiply lensed emission (i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Model of each slice in \Fig{model} thus provides
properties on the intrinsic kinematics. The slices
are obtained by binning the data (over the full linewidth
$\sim$700\kms; see \Sec{CO21}) by five channels (i.e., into seven slices)
 to increase the SNR.

The lens mass distribution is modeled using a singular isothermal
ellipsoid (SIE) profile, which is described by five free parameters: the
positional offset in R.A. and Dec. relative to an arbitrary chosen
fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
position angle. We use the VLA radio continuum emission toward
the foreground galaxy to initialize the positional offset. We impose a
uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec., which is
motivated by the astrometry uncertainties in the VLA image as well as
the uncertainties provided by previous SIE lens model (C06).
We initialize the Einstein Radius based on the model parameters reported by C06
and impose a uniform prior using $\pm$3$\sigma$ of their uncertainties.
The sources are modeled using elliptical Gaussian profiles, which are
parameterized by six free parameters: the positional offset in R.A.
and Dec. relative to the lens, the intrinsic flux density, the effective
radius, the axial ratio, and the position angle. The position of each source
is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
and the effective radius is allowed to vary from 0\farcs01$-$2".

% Check with Shane
Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF). In each model, we employ
$\sim$100,000 samples as the initial ``burn-in'' stage to stabilize the Markov
chains (which we then discard). We use the final $\sim$5,000
samplings to determine the posterior probability distributions. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

We first obtain a preliminary lens model for each channel slice independently,
where their lens parameters are allowed to vary and are initialized according
to the aforementioned way. We obtain the final model
by repeating the modeling over each slice but fixing their lens parameters
according to the overall median in the preliminary models,
as listed in \Tab{lens}.
This ensures that all models share the same lens profile.
The magnification factors in \Tab{model} are determined by taking the ratio
between the image plane flux and the source plane flux of each model.

@@

\subsubsection{Interpretation and Caveats} \label{sec:caveat} %DONE
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient across the source plane, which is
indicative of a disk geometry. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

@@

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
\input{table_magFactor}
Previous lens models of RXJ1131 find conspicuous
differential lensing effect across {\it HST}
H-Band, V-band, and I-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission, arising from \SF.
The highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO, where the red wing
of \bco is apparently much brighter than that in the blue wing, consistent
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).

\subsection{\bco Dynamical modeling} \label{sec:dynamics} %DONE
This section proceeds under the assumption that RXJ1131 is
a rotating disk (see previous sections).
Assuming the velocities of the respective lens models
correspond to solely the tangential component (i.e., $\theta$ = 0), we extract
a pseudo PV diagram along the major axis in \Fig{PV} by slicing across their
source plane positions. The best-fit major axis is along PA of 121\degr.

We attempt to characterize the molecular gas kinematics using an empirically motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rotation curve becomes flat.
We perform non-linear least square fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on Monte Carlo simulation
of 500 iterations, which we perturb the input parameters according to a random
Gaussian distribution of sigma corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
$R_{t}$\,=\,10.6\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
We note, however, that since emission is not detected beyond the flat regime
of the rotation curve, the asymptotic velocity is poorly constrained.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.

\begin{figure}[!Htbp]
\centering
\includegraphics[width=0.455\textwidth]{../Figures/bestfit_PV.eps}
\caption{PV slice along the major axis in the source plane at PA\,=\,121\degr.
Dashed line shows the best-fit rotation curve using an arctangent model.
DR may suggest include MC simulation fits, maybe I will do that later.
 \label{fig:PV}}
\end{figure}

We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is inequivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
Studies of the Tully-Fisher relation typically use V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$) as the rotation velocity ($V_{\rm max}$ in their
terminology), which corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3 kpc inferred from the C06 lens model (converted to
our cosmology), who use all {\it HST} H--, V--, and I--bands in their
modeling. If only V$-$band is used, the half-light radius is $\sim$4kpc \citep{Brewer08a}.
This discrepancy arises owning to the exclusion of the more diffused emission in the V-band
(\ie V-band is missing the diffused emission).
This indicates that the molecular gas may be ... (see \Sec{size}). DR: ok, let's discuss this.

Using this $V_{\rm rot}$, we find a dynamical mass of
$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 17\E{10}\,\Msun.
If we instead consider the line peak separation from the
\bco line profile $\Delta v_{\rm sep}/2 \sim$110\,\kms, we find
$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 1.8\E{10}\,\Msun.
DR: here, I list the extrema for possible Mdyn given our data,
should I say anything more?
We correct for the inclination effect using the
morphological axial ratio from the reconstructed image (Figure 3 in C06), where
the minor axis is 1\farcs8 and the major axis is 3\farcs25.
We thus find an inclination angle of 56.4\degr, which is consistent with the
observed unobscured AGN and an observable double peak line profile.
The dynamical mass is then 2.5\E{10}\Msun$<$$M_{\rm dyn}$($<$6 kpc)$<$25\E{10}\Msun.
We caution that this analysis is based on limited spatial
resolution data and will be verified by future higher-resolution
observations.

\subsection{SED modeling} \label{sec:SED}
We extrapolated a power-law to 24 \micron to decompose the flux
at 24 \micron in MIPS.
%
%We fit modified blackbody functions to
%to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt 
%BLAH (rest frame; Dunne et al. 2003).)
%We added blah\% calibration uncertainties on the PdBI data.
%
%We check convergence of our chains by requiring that the autocorrelation length for each model parameter is 
%several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
%The code treats the instrument response. 
%
%% upper limit using decomposed 24 um
%% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
%The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
%% parameter estimation problem
%For these parameter estimation problems using MCMC to sample,
%the full answer is the full joint posterior PDF.
%We here report the summary statistics (global mode (where min. chi),
%marginal mode (in log file),
%posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.

\subsection{ISM properties}
We correct for lensing magnification using the median among our models ($\mu_{\rm L}$=BLAH).
Assuming a Salpeter initial mass function, we find the SFR of blah using the \fir luminosity after corrected for lensing .
\subsection{Gas Mass}
\subsection{Source Extent} \label{sec:size}
Compared to HST:

@@

As discussion in previous sections, while we see evidence such as a symmetric velocity field in the source plane, double-horned profile, observed velocity
gradient, C06 model $n$=1 Sersic profile, which suggest that RXJ1131 is likely a rotating disc. Yet, this is insufficient to conclude a disk morphology. Additional characteristics such as peak velocity dispersion at the central region and a ``spider'' diagram are needed, which is commonly seen in local spirals.
